\textbf{ Mapping stellar surfaces\\ I: Degeneracies in the rotational light curve problem }

### 2021-01-25 paper1/ms.tex
finished section 2

@@

The present paper is also similar to \citet{Walkowicz2013} and
\citet{Basri2020}, who explored the information content of
stellar light curves from a large set of simulated spotted stellar
surfaces. While our paper is largely complementary to
that work, we instead approach the information content problem from
a purely theoretical---as opposed to empirical---point of view.
%
The present paper is the first in a series dedicated to the development of
techniques to perform robust inference about stellar surfaces from
unresolved photometric and spectroscopic measurements. The results
of this paper serve as the starting point for the development of
an interpretable Gaussian process for the ensemble analysis of
stellar light curves, which is the subject of Paper II \citep{PaperII}.

@@

There are three major points that make the kind of ensemble
analyses discussed above difficult in practice. First, and perhaps
most obviously, stars are
not identical, no matter how ``similar'' we think they may be.
Even stars of the same spectral type, age, and metallicity will
in general have different configurations of spots on their surfaces.

In practice, the fact that stars are not identical complicates this picture.
We can still learn about the \emph{distribution} of spot properties, but
in general our ensemble must consist of far more light curves in order to
place strong constraints on these properties. As we
show \xxx{in the next paper},
under ideal conditions an ensemble of $M = 50$ similar stars may be sufficient,
but in practice we may need on the order of hundreds or even a thousand light curves
in order to mitigate the effects of variance in the sample.

Also, we don't know the inclinations.

>>>>

\defcitealias{PaperII}{Paper II}

@@

The present paper is also similar to \citet{Walkowicz2013} and
\citet{Basri2020}, who explored the information content of
stellar light curves from a large set of simulated spotted stellar
surfaces. While our paper is largely complementary to
that work, we instead approach the information content problem from
a purely theoretical---as opposed to empirical---point of view.
%
The present paper is the first in a series dedicated to the development of
techniques to perform robust inference about stellar surfaces from
unresolved photometric and spectroscopic measurements. The results
of this paper serve as the starting point for the development of
an interpretable Gaussian process for the ensemble analysis of
stellar light curves, which is the subject of
\citepalias[\citealt{PaperII}, hereafter][]{PaperII}.

@@

There are three major points that make the kind of ensemble
analyses discussed above difficult in practice. First, and perhaps
most obviously, stars are
not identical, no matter how ``similar'' we think they may be.
Even stars of the same spectral type, age, and metallicity will
in general have different configurations of spots on their surfaces.
When we perform an ensemble analysis on the light curves of a
heterogeneous group of stars, we are learning something about the
\emph{distribution} of surface properties across all the stars in
the sample---not the surface properties of any individual star.
What exactly we can learn in this case is not immediately obvious,
and requires a detailed investigation. This is the subject of
the next paper in this series \citepalias{PaperII}, where we show that,
armed with a good model,
we can learn \emph{a lot} about the distribution of starspot
properties of a heterogenous group of stellar light curves.

The second point is that while observing many stars at different
inclinations breaks many of the degeneracies at play, our analysis
above assumed we knew what the values of the inclinations were.
In practice, this will usually not be the case. While we may have
good priors for some stars (from spectroscopic $v\sin i$ measurements,
or from the assumption that transiting exoplanet hosts are likely
to have inclinations close to $I=90^\circ$), for the vast majority
of field stars we won't know much a priori. Since the inclination
is typically degenerate with the spot latitude \citep[e.g.,][]{Walkowicz2013},
this decreases the constraining power of ensemble analyses.
However, as we show in \citetalias{PaperII}, there is still enough
information in a large ensemble to independently constrain the spot latitudes
and the \emph{individual} stellar inclinations.

The final point concerns limb darkening, which also has a strong
effect on the structure of the null space. While limb darkening can
help us by breaking degeneracies, in practice it is likely to be more
of a problem, since the use of incorrect limb darkening coefficients can lead
to bias in the spot properties when doing inference.
It is therefore extremely important to use reliable limb darkening models
when doing ensemble analyses; we also explore this in \citetalias{PaperII}.
